Inefficient Concessions and Mediation

### 2021-02-01 draft.tex
remove claim about effect of 0<e<1 on high type IC

Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$. As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$. This is not at all obvious though, especially because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}

@@

Using the mediation mechanism $M$ with $e=0.29$ and $g=12.98$, we satisfy both the low type constraint that $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$. Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.

		\item[(b)] Let $T = 1$, $W=1$ and $D = 1$. The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$. Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$. By Theorem~\ref{theorem:2}, separation through concessions is possible.

>>>>

Lemma~\ref{lemma:efficiency} implies that the high types will either prefer $e=1$ or $e=0$. As we turn to our result about incentive compatibility when concessions have material value, we focus on these two cases as the most focal and easiest upon which to coordinate.\footnote{For some parameter values, we cannot rule out that a \emph{concessions separating equilibrium} with $0<e<1$ exists and improves upon high type welfare when high types are patient enough to separate when $e=0$ but not when $e=1$.} %This is not at all obvious because increasing $e$ from $0$ can tighten the high type's incentive compatibility constraint.}

@@

Using the mediation mechanism $M$ with $e=0.29$ and $g=12.98$, we satisfy both the low type constraint that $g\geq \frac{\left(1 - \de_l \right)\left(T +D \right)}{p - e\left(p +(1-\de_l)T +W \right)}=9.5890411$ and the high type constraint $g\leq \frac{ T + D - W}{Te - (1-\de_h)(1-e)}=12.987013$. Welfare is 5.0768, compared to 2.82 in the \emph{concessions separating equilibrium with inefficient gifts}.
		\item[(b)] Let $T = 1$, $W=1$ and $D = 1$. The assumption that $T > W - D$ is satisfied, and the threshold for high types to separate through concessions when the future material value of concessions is destroyed is $\de = \frac{1}{1+1} = .5$. Let $\de_h = \frac{15}{16}=0.9375$ and $\de_l = .5$ and $p = .5$. By Theorem~\ref{theorem:2}, separation through concessions is possible.
